\maketitle

\begin{abstract}
Industry 4.0 is a title for the current trend of automation, scaling and data exchange in manufacturing technologies. It includes artificial intelligence, virtual reality, the Internet of things and Big Data analysis. Genomics is a vivid representative of the industry 4.0 that requires solving many urgent problems, such as storage and analysis of Big Data with keeping public access for researchers and privacy for people.

Currently there is a problem of inequality in the genome industry. It means that the main part of personal genomic data was concentrated in data centers of genomic corporations, government, scientific and medical institutions and pharmaceutical companies. Moreover, there is an issue of legal limitation of access to personal genomic data, as well as the absence of possibility for genomic data management and sharing. This genomic data monopolization dramatically inhibits the development in a number of scientific and medical fields.

The development of cryptocurrencies and blockchain-based technologies leads to significant transformation of many economical domains. Application of blockchain approach will be a lifeline allowing to upgrade the development of personal genomics. It will make each person the owner of his or her genetic data.

The Zenome project is a decentralized blockchain-driven database of genomic information. This platform supports the possibility to manage your genomic data while maintaining privacy and ability to make a profit from selling access to different parts of the genome. It will establish equal conditions for drug development and for the progress of scientific and medical technologies.

Zenome is a new economic environment based on genomic data and blockchain technology. The implementation of our conceptual model will solve the following difficulties:
\begin{itemize}[nosep]
\item Creating an infrastructure for storing Big genomic data using distributed database
\item Open access to millions of human genomes worldwide with privacy protection
\item Possibility for each person to participate in scientific and clinical research and to make profit from this
\item Stimulating the enhancement of genomic sciences in developing countries and de-monopolization of genomic data in developed countries
\end{itemize}

%This paper:
%\begin{itemize}[nosep]
%\item Introduces main concepts of contemporary genomics and discusses problems associated with them
%\item Explains the conceptual design of new distributed genomic database that actually represents a new economic model based on genomics
%\item Proposes the solutions for keeping privacy while enabling public access to genomic data for the scientific community
%\item Explains the ranking approach for storing and recording genomic data in order to minimize the risks of malicious attacks
%\end{itemize}

\end{abstract}
